Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-04-10 main.tex
tightened up statement of identity coloring; fixed a few typos

A {\em contour} $\contour \in \CONTOURS = \COMPONENTS \rightarrow
\{\HIGHSEC, \LOWSEC\} \times \{\HIGHINT, \LOWINT\}$ is a map from
machine components to a pair of confidentiality and integrity labels.
$\LOWSEC$ marks locations whose contents represent data observable
{\em by the current process}; $\HIGHSEC$ corresponds to non-observable
data (e.g. local state of the process caller). $\HIGHINT$ marks
locations that the current process does not have write access to;
$\LOWINT$ is freely accessible memory. As examples of different
combinations consider the following:
\begin{itemize}
\item Locations that belong to the current process such as
  available registers, local stack, memory accessible through
  available pointers will be tagged $\LOWSEC \times \LOWINT$:
  they can be both read and written.
\item The local state of the caller that needs to be protected from a
  potentially untrusted callee will be marked $\HIGHSEC \times
  \HIGHINT$. The callee should be able to neither read nor write
  these locations.
\item The instruction memory is read only for every process: $\LOWSEC
  \times \HIGHINT$.
\item We won't have examples of secret data that can be overwritten.
  \leo{Maybe in the lazy setting?}
\end{itemize}

@@

Given a machine trace $\seq{\mach}$ and a call map this can be
computed as follows:
\begin{enumerate}
\item $mach_0$ is colored $\ME$.
\item Find the next machine state $\mach_c$ (if any) that appears in
  the trace $\seq{mach}$ such that the instruction executed at
  $\mach_c$ is a $JAL$ that is marked as a call in the call map.
\item Color all states between $\mach_0$ and $\mach_c$ inclusive as
  $\ME$. If no such state exists, color the remainder of the trace
  $\ME$.
\item Find the next state $\mach_r$ after $\mach_c$ in the trace (if
  any) such that the pc of $\mach_r$ is equal to the pc of $\mach_c +
  4$, and whose stack pointer is identical to that of $\mach_c$.
\item Color all states between $\mach_{c+1}$ and $\mach_r$ as
  $\NOTME$.  If no such state exists, color the remainder of the trace
  $\NOTME$.
\item Color $\mach_{r+1}$ as $\ME$. Go to step (2).
\end{enumerate}

@@

Given a contour $C$ and a machine state $M$, the {\em contoured trace}
induced by $C$ and $M$, written $\induced{C}{M}$, is the (finite or
infinite) sequence of pairs of (contour, machine state) pairs in which
states in adjacent pairs are related by $\stepstounderfull$, and in which
contours in adjacent pairs are constructed as follows:
\begin{itemize}
\item If in the identity coloring of $\seq{\mach}$ $\ID_i$ = $\ID_{i+1}$ then
  $C_{i+1} = C_i$.
\item If $\ID_{i} = \ME$ and $\ID_{i+1} = \NOTME$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of $\mach_i$ (the
  caller) to $\HIGHSEC \times \HIGHINT$.
\item If $\ID_{i} = \NOTME$ and $\ID_{i+1} = \ME$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of the caller
  to $\LOWSEC \times LOWINT$.
\end{itemize}
\leo{To make this more precise we need to accurately describe what
  local state {\em is}}

>>>>

A {\em contour} $\contour \in \CONTOURS = \COMPONENTS \rightarrow
\{\HIGHSEC, \LOWSEC\} \times \{\HIGHINT, \LOWINT\}$ is a map from
machine components to a pair of confidentiality and integrity labels.
$\LOWSEC$ marks locations whose contents represent data observable
{\em by the current process}; $\HIGHSEC$ corresponds to non-observable
data (e.g. local state of the process caller). $\HIGHINT$ marks
locations that the current process does not have write access to;
$\LOWINT$ is freely accessible \apt{``accessible''?} memory. As examples of different
combinations consider the following:
\begin{itemize}
\item Locations that belong to the current process such as
  available registers, local stack, memory accessible through
  available pointers will be tagged $\LOWSEC \times \LOWINT$:
  they can be both read and written.
\item The local state of the caller that needs to be protected from a
  potentially untrusted callee will be marked $\HIGHSEC \times
  \HIGHINT$. The callee should be able to neither read nor write
  these locations.
\item The instruction memory is read only for every process: $\LOWSEC
  \times \HIGHINT$.
\item We won't have examples of secret data that can be overwritten.
  \leo{Maybe in the lazy setting?}
\end{itemize}

@@

Given a machine trace $\seq{\mach}$ and a call map the identity coloring can be
computed as follows:
\begin{enumerate}
\item Set $i=0$.
\item Color $\mach_i$ as $\ME$.
\item Find the next machine state $\mach_c$ (if any) that appears in
  the trace $\seq{\mach}$ such that the instruction executed at
  $\mach_c$ is a $JAL$ that is marked as a call in the call map.
\item Color all states between $\mach_i$ and $\mach_c$ inclusive as
  $\ME$. If no such state exists, color the remainder of the trace
  $\ME$.
\item Find the next state $\mach_r$ after $\mach_c$ in the trace (if
  any) such that the pc of $\mach_r$ is equal to the pc of $\mach_c +
  4$, and whose stack pointer is identical to that of $\mach_c$.
\item If $M_r$ exists, color all states between $\mach_{c+1}$ and $\mach_{r-1}$ inclusive as
  $\NOTME$. Otherwise, color the remainder of the trace starting from $\mach_{c+1}$ as $\NOTME$.  
\item If $M_r$ exists, set $i=r$ and go to step (2). Otherwise, halt.
\end{enumerate}

@@

Given a contour $C$ and a machine state $M$, the {\em contoured trace}
induced by $C$ and $M$, written $\induced{C}{M}$, is the (finite or
infinite) sequence of pairs of (contour, machine state) pairs in which
states in adjacent pairs are related by $\stepstounderfull$, and in which
contours in adjacent pairs are constructed as follows:
\begin{itemize}
\item If in the identity coloring of $\seq{\mach}$ $\ID_i$ = $\ID_{i+1}$ then
  $C_{i+1} = C_i$.
\item If $\ID_{i} = \ME$ and $\ID_{i+1} = \NOTME$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of $\mach_i$ (the
  caller) to $\HIGHSEC \times \HIGHINT$.
\item If $\ID_{i} = \NOTME$ and $\ID_{i+1} = \ME$, then $C_{i+1}$ is
  constructed from $C_i$ by setting the local state of the caller
  to $\LOWSEC \times \LOWINT$.
\end{itemize}
\leo{To make this more precise we need to accurately describe what
  local state {\em is}}

\apt{How is this definition of contoured traces connected to the various properties
  below (which seem to talk about an (uncontoured) trace plus a single contour) ?}
